Natural Stories model analyses

### 2022-08-10 Analysis/models.Rmd
Roger touched

```{r meaned data, eval=T, cache=T}
gam_ngram_1 <- gam(formula_interact, data=ngram_mean_data, method="REML")
gam_grnn_1 <- gam(formula_interact, data=grnn_mean_data, method="REML")
gam_txl_1 <- gam(formula_interact, data=txl_mean_data, method="REML")
gam_gpt_1 <- gam(formula_interact, data=gpt_mean_data, method="REML")
gam_gpt_1a <- gam(formula_interact, data=filter(gpt_mean_data,len<9), method="REML")
gam_gpt_2 <- gam(formula2_interact, data=gpt_mean_data, method="REML")
gam_gpt_3 <- gam(formula3_interact, data=gpt_mean_data, method="REML")
print(plot(getViz(gam_gpt_1x)))
print(plot(getViz(gam_gpt_3)))

@@

>>>>

```{r meaned data, eval=T, cache=T}
gam_ngram_1 <- gam(formula_interact, data=ngram_mean_data, method="REML")
gam_grnn_1 <- gam(formula_interact, data=grnn_mean_data, method="REML")
gam_txl_1 <- gam(formula_interact, data=txl_mean_data, method="REML")
gam_gpt_1 <- gam(formula_interact, data=gpt_mean_data, method="REML")
gam_gpt_1a <- gam(formula_interact, data=filter(gpt_mean_data,len<9), method="REML")
gam_gpt_2 <- gam(formula2_interact, data=gpt_mean_data, method="REML")
gam_gpt_3 <- gam(formula3_interact, data=gpt_mean_data, method="REML")

@@

#print(plot(getViz(gam_gpt_1a)))
print(plot(getViz(gam_gpt_no_interact)))
print(plot(getViz(gam_gpt_2)))
summary(gam_gpt_3)
